Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-06 Latex/tex/pr.tex
complete more for latex file of icc

\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k}+ \boldsymbol{z}_{\mathcal{U}_v}

@@

Furthermore, $\zeta_{U_v,k} \delequal \{\zeta_{u(v,1),k},\zeta_{u(v,2),k},...,\zeta_{u(v,N_{U_v}),k}\}$,
$\zeta_{u(v,i),k} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.

@@

where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(a_{r_{(s,1),u_{(v,i)}}},\ldots,a_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$

@@

 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n}\zeta_{u_(v,l),n}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n}\zeta_{u_(y,l),n}}_{\text{(inter-service interference)}}\\

@@

\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}x_{s,d}\phi

@@

Where, $x_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{X} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{X})} \\

@@

& \sum_{d=1}^{D_c}\sum_{v=1}^{V}x_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} x_{s,d} \tau_d                       && \quad \forall f, \forall s 

@@

Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{X} =[x_{s,d}]  \forall s , \forall d $.

@@

\min\limits_{\boldsymbol{X} }   \quad &   \phi_{tot}(\boldsymbol{X})\\

@@

\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
\State Set the iteration index $i = 1$ and begin the iteration (Outer
Loop).

>>>>

\bold{y}_{U_v} = \sum_{k=1}^{N_k}\sum_{s = 1}^{N_s} \boldsymbol{H}^H_{\mathcal{R}_s,\mathcal{U}_v}(\boldsymbol{W}_{\mathcal{R}_s,\mathcal{U}_v}\boldsymbol{P}_{U_v}^{\frac{1}{2}}\boldsymbol{x}_{\mathcal{R}_s}+ \boldsymbol{q}_{R_s}) \zeta_{U_v,k,s}+ \boldsymbol{z}_{\mathcal{U}_v}

@@

Furthermore, $\zeta_{U_v,k,s} \delequal \{\zeta_{u(v,1),k,s},\zeta_{u(v,2),k,s},...,\zeta_{u(v,N_{U_v}),k,s}\}$,
$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.

@@

where $\boldsymbol{g}_{\mathcal{R}_s,u_{(v,i)}} \backsim \mathcal{N}(0,N_0\boldsymbol{I}_{\mathcal{U}_v})$ indicates the fast fading and flat fading channel vector and $\boldsymbol{\beta}_{\mathcal{R}_s,u_{(v,i)}}=\text{diag}(b_{r_{(s,1),u_{(v,i)}}},\ldots,b_{r_{(s,\mathcal{R}_s),u_{(v,i)}}})$

@@

 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{u_{(v,l)}}a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{u_{(y,l)}}a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\

@@

\phi_{tot} = \sum_{s=1}^{S}\sum_{d=1}^{D_c}y_{s,d}\phi

@@

Where, $y_{s,d}$ is a binary variable which indicates whether $d^{th}$ data-center is mapped to VNFs of $s^{th}$ slice or not.\\

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\

@@

& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                       && \quad \forall f, \forall s 

@@

Where,$\boldsymbol{P} =[p_{u(v,k)}]  \forall v , \forall k $, $\boldsymbol{A} =[a_{vs}]  \forall v , \forall s $ and $\boldsymbol{Y} =[y_{s,d}]  \forall s , \forall d $.

@@

\min\limits_{\boldsymbol{y} }   \quad &   \phi_{tot}(\boldsymbol{Y})\\

@@

\State Set the maximum number of iterations $I_{max}$
